I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-08 Paper/Paper_noProof.tex
Writing

@@

We compare our method to two famous verifiers (their incomplete mode): PRIMA and $\beta$-Crown on 5 typical MNIST models. Basically, our method can exceed PRIMA on both accuracy and speed, and exceed $\beta$-Crown on accuracy.

>>>>

\[
\begin{array}{c|c|cc|cc|cc|cc}

	\text{Network}  & \varepsilon&  \multicolumn{2}{@{}c@{}|}{\text{Comp(fast)}} & \multicolumn{2}{@{}c@{}|}{\text{PRIMA}} &  \multicolumn{2}{@{}c@{}|}{\text{Comp(slow)}} & \multicolumn{2}{@{}c@{}|}{\text{beta-Crown}}  \\

  &  & \mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) &\mathrm{Ver}.\% & \mathrm{Time}(s) & \mathrm{Ver}.\% & \mathrm{Time}(s) \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

	\mathrm{MLP}\ 5\times100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline
\end{array}
\]

@@

In Table 3, we compare against two representative incomplete
verifiers on 4 MLP networks for MNIST under the same
set of 1000 images. beta-Crown is the state-of-the-art verifier based on branch-and-bound. PRIMA is another strong and representative method based on multi-neuron linear relaxation.
